Home

### 2025-07-20 index.qmd
Update website content and structure
Renamed sections in various files for clarity, changing 'Bin Yu' to 'Professor Bin Yu' in index.qmd and 'Select Publications' to 'Papers' in papers.qmd. Enhanced publication entries with direct links to papers for better accessibility. Updated the 'People' section title in people.qmd and changed 'Code' to 'Software' in software.qmd for consistency. Removed the outdated bio1.jpg image file.
Update website content and layout
Changed the page footer in _quarto.yml to center the copyright notice for 2025. Revised the 'About' page in about.qmd to enhance clarity

# Bin Yu

<div style="flex: 0 0 200px;">
<img src="images/binyu.jpg" alt="Bin Yu" style="width:200px; border-radius:8px;" />
</div>

- Chancellor's Distinguished Professor of Statistics
- Statistics Department Chair, 2009 - 2012
- Professor by courtesy, Electrical Engineering and Computer Sciences

**Address:** 367 Evans Hall #3860, Berkeley, CA 94720  
**Phone:** 510-642-2781  
**Fax:** 510-642-7892  
**Email:** [binyu@berkeley.edu](mailto:binyu@berkeley.edu)

@@

- *2025* [New paper: PCS workflow for veridical data science in the age of AI (Z. Rewolinski and B. Yu, 2025)](https://www.stat.berkeley.edu/~yugroup/pubs/pcs_workflow-6.pdf)
- *2025* [Veridical Data Science in Biology on July 11, 2025 at UC Berkeley (Submission deadline July 4)](https://www.eventbrite.com/e/veridical-data-science-for-biology-2025-tickets-1384456339179)
- *2025* [Rome Workshop on Veridical Data Science, June 20, 2025](https://www.integreat.no/events/public-events/workshops/veridical-data-science.html)
- *2024* [Veridical data science and medical foundation models](https://arxiv.org/abs/2409.10580) on arXiv by Alaa and Yu.
- *2024* [VDS book review](https://hdsr.mitpress.mit.edu/pub/5322mn1e/release/3) by Yuval and Yoav Benjamini in Harvard Data Science Review (HDSR)-- "pedagogical excellence, diverse examples, and projects make Veridical Data Science a suitable textbook for students of all levels, in addition to being a valuable resource for data scientists in general" (review summary in HDSR Editor-in-Chief's note), June, 2024.
- *2024* [Inaugural Berkeley-Stanford Workshop on Veridical Data Science at UC Berkeley](https://na.eventscloud.com/website/69057/) (May 31, 2024) ([talk videos available](https://www.youtube.com/playlist?list=PLKW2Azk23ZtSrg4jwLSioaV1bwmFnQ1Bx))
- *2024* Our MIT Press book ["Veridical Data Science: The Practice of Responsible Data Analysis and Decision Making"](https://mitpress.mit.edu/9780262049191/veridical-data-science/), has been released [online](http://vdsbook.com/).
- *2023* ["Veridical data science towards trustworthy AI"](https://ww2.amstat.org/meetings/jsm/2023/webcasts/index.cfm) (Talk video of COPSS DAAL (formerly Fisher Award and Lecture), scroll down), Aug. JSM in Toronto, 2023.
- *2023* IMS Wald [Lecture I](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1029) and [Lecture II](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1031), and [COPSS Distinguished Award and Lecture (DAAL)](https://ww2.aievolution.com/JSMAnnual/index.cfm?do=ev.viewEv&ev=1374) delivered at [Joint Statistical Meeting (JSM)](https://ww2.amstat.org/meetings/jsm/2023/) in Toronto, August 2023
- *2022* [CDSS news: Statistics-Computer Science team reflects on tackling covid outbreaks](https://data.berkeley.edu/news/statistics-computer-sciences-team-reflects-tackling-covid-outbreaks), May, 2022
- *2021* Honorary Doctorate, University of Lausanne (UNIL) (Faculty of Business and Economics), June 4, 2021 ([Interview of Bin Yu](https://www.youtube.com/watch?v=1JRGPGhcYzU) by journalist Nathalie Randin, with an introduction by Dean Jean-Philippe Bonardi of UNIL in French ([English translation](https://www.stat.berkeley.edu/~binyu/Intro-DeanBonardi-UNIL.pdf)))
- *2020* [Veridical data science](https://www.pnas.org/content/117/8/3920) (PCS framework: [v-flow code](https://github.com/Yu-Group/veridical-flow) and [documentation template](https://yu-group.github.io/vdocs/PCSDoc-Template.html)), PNAS, 2020 ([QnAs with Bin Yu](https://www.pnas.org/content/117/8/3893))
- *2020* [CDSS news on our PCS framework: "A better framework for more robust, trustworthy data science"](https://data.berkeley.edu/people/bin-yu), Oct. 2020
- *2020* [UC Berkeley to lead $10M NSF/Simons Foundation program to investigate theoretical underpinnings of deep learning](https://data.berkeley.edu/news/uc-berkeley-lead-10m-nsfsimons-foundation-program-investigate-theoretical-underpinnings-deep), Aug. 25, 2020
- *2020* UC Berkeley team part of the new NSF AI Center for Cybersecurity [ACTION](https://action.ucsb.edu/) led by UCSB.

>>>>

:::: {.columns}

::: {.column width="40%"}
![](images/binyu.jpg)
:::

::: {.column width="60%"}
## Professor Bin Yu

Chancellor's Distinguished Professor of Statistics  
Statistics Department Chair, 2009 - 2012  
Professor of Electrical Engineering and Computer Sciences, by courtesy

## Contact

Address: 367 Evans Hall #3860, Berkeley, CA 94720  
Phone: 510-642-2781  
Fax: 510-642-7892  
Email: [binyu@berkeley.edu](mailto:binyu@berkeley.edu)
:::

::::

@@

- <span class="year-entry">2025</span>[PCS workflow for veridical data science in the age of AI](https://www.stat.berkeley.edu/~yugroup/pubs/pcs_workflow-6.pdf) - Framework for responsible AI development and deployment
- <span class="year-entry">2025</span>[Veridical Data Science in Biology workshop](https://www.eventbrite.com/e/veridical-data-science-for-biology-2025-tickets-1384456339179), UC Berkeley, July 11 - Applying trustworthy data science to biological research
- <span class="year-entry">2025</span>[Rome Workshop on Veridical Data Science](https://www.integreat.no/events/public-events/workshops/veridical-data-science.html), June 20 - International workshop on responsible data analysis
- <span class="year-entry">2024</span>[Veridical data science and medical foundation models](https://arxiv.org/abs/2409.10580) - Guidelines for trustworthy medical AI systems
- <span class="year-entry">2024</span>[Mechanistic Interpretation through Contextual Decomposition in Transformers](https://arxiv.org/pdf/2407.00886) - Method for understanding transformer decision-making processes
- <span class="year-entry">2024</span>[LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354) - Improved technique for fine-tuning large language models
- <span class="year-entry">2024</span>[VDS book review](https://hdsr.mitpress.mit.edu/pub/5322mn1e/release/3) in Harvard Data Science Review - Praise for pedagogical approach to responsible data science
- <span class="year-entry">2024</span>[Berkeley-Stanford Workshop on Veridical Data Science](https://na.eventscloud.com/website/69057/) ([videos](https://www.youtube.com/playlist?list=PLKW2Azk23ZtSrg4jwLSioaV1bwmFnQ1Bx)) - Inaugural academic collaboration on trustworthy AI
- <span class="year-entry">2024</span>[Veridical Data Science book](https://mitpress.mit.edu/9780262049191/veridical-data-science/) released ([online](http://vdsbook.com/)) - Comprehensive guide to responsible data analysis and decision making
- <span class="year-entry">2023</span>[Explaining black box text modules in natural language with language models](https://arxiv.org/abs/2305.09863) - Natural language explanations for neural network text processing
- <span class="year-entry">2023</span>[Diagnosing transformers: illuminating feature space for clinical decision-making](https://arxiv.org/abs/2305.17588) - Interpretability methods for medical transformer applications
- <span class="year-entry">2023</span>[COPSS Distinguished Award and Lecture](https://ww2.amstat.org/meetings/jsm/2023/webcasts/index.cfm), JSM Toronto - Recognition for contributions to statistical science and AI
